---
title: Prof Evals
author: ''
date: '2022-02-28'
slug: prof-evals
categories: []
tags: []
---
## Downloading and opening libraries
```{r}
library(tidyverse)
library(moderndive)
library(skimr)
library(gapminder)
```

## Opening data
```{r}
evals_ch5 <- evals %>%
  select(ID, score, bty_avg, age)
glimpse(evals_ch5)
# doubles and integers
```
```{r}
evals_ch5 %>%
  sample_n(size = 5)
# random sample of 5 arguments of each column, different each time it is run
```

# Central Measures of Tendancy
```{r}
evals_ch5 %>%
  summarize(mean_bty_avg = mean(bty_avg), mean_score = mean(score),
            median_bty_avg = median(bty_avg), median_score = median(score))
# a smaller skew is present
```
# Regression values
```{r}
evals_ch5 %>% select(score, bty_avg) %>% skim()
#  skim() takes in a data frame, “skims” it, and returns commonly used summary statistics
```

# Scatter plot of Score vs Bty_avg
```{r}
plot(evals_ch5$score, evals_ch5$bty_avg)

```
```{r}
ggplot(evals_ch5, aes(x = bty_avg, y = score))+
  geom_point() +
  labs(x = "Beauty Score",
       y = "Teaching Score", 
       title = "Scatterplot of relatioinship of teaching and beauty scores")
```
> To differentiate between overlapping points, use jitter plot  

```{r}
ggplot(evals_ch5, aes(x = bty_avg, y = score)) +
  geom_jitter() +
  labs(x = "Beauty Score", y = "Teaching Score",
       title = "Scatterplot of relationship of teaching and beauty scores")
```

### Getting correlation
```{r}
evals_ch5 %>%
  get_correlation(formula = score ~ bty_avg)
# ~ is tilde
```
> Using summarize   

```{r}
evals_ch5 %>%
  summarize(correlation = cor(score, bty_avg))
```
## Correlation showing in graph
```{r}
ggplot(evals_ch5, aes(x = bty_avg, y = score)) +
  geom_point() +
  labs(x = "Beauty Score", y = "Teaching Score",
       title = "Relationship between teaching and beauty scores") +  
  geom_smooth(method = "lm", se = FALSE)
# lm is linear model bar giving line of best fit, se is standard error bars
```
> moderndrive package has score_model() and get_regression_table() 
>> is used to attain the b0 intercept and the bty_avg slope aka. **linear regression table**  

```{r}
# Fit regression model:
score_model <- lm(score ~ bty_avg, data = evals_ch5)
# Get regression table:
get_regression_table(score_model)
```
```{r}
regress_points <- get_regression_points(score_model)
regress_points
```
score_hat = corresponding value on the regression line for the x values  
residual = y - yhat = vertical distances between points and regression line  

# Exploratory data analysis

```{r}
gapminder2007 <- gapminder %>%
  filter(year == 2007) %>%
  select(country, lifeExp, continent, gdpPercap)
glimpse(gapminder2007)
```
```{r}
gapminder2007 %>% sample_n(size = 5)
gapminder2007 %>%
  select(lifeExp, continent) %>%
  skim()
# summary stats
```
## Bar plot
```{r}
ggplot(gapminder2007, aes(x = lifeExp)) +
  geom_histogram(binwidth = 5, color = "white") +
  labs(x = "Life expectancy", y = "Number of countries",
       title = "Histogram of distribution of worldwide life expectancies")
```
> add facet wrap  

```{r}
ggplot(gapminder2007, aes(x = lifeExp)) +
  geom_histogram(binwidth = 5, color = "white") +
  labs(x = "Life expectancy", 
       y = "Number of countries",
       title = "Histogram of distribution of worldwide life expectancies") +
  facet_wrap(~ continent, nrow = 2)
# separates graphs based on continent
```
## Boxplot
```{r}
ggplot(gapminder2007, aes(x = continent, y = lifeExp)) +
  geom_boxplot() +
  labs(x = "Continent", y = "Life expectancy",
       title = "Life expectancy by continent")
```

## Measures of central tendency
```{r}
lifeExp_by_continent <- gapminder2007 %>%
  group_by(continent) %>%
  summarize(median = median(lifeExp), 
            mean = mean(lifeExp))

lifeExp_by_continent
```

### Regression stats
> “fit” the linear regression model using the lm(y ~ x, data) function and save it in lifeExp_model  
> get the regression table by applying the get_regression_table() function from the moderndive package to lifeExp_model.  

```{r}
lifeExp_model <- lm(lifeExp ~ continent, data = gapminder2007)
get_regression_table(lifeExp_model)
# lm(y ~ x, data)
```
```{r}
# Compute sum of squared residuals
regression_points <- get_regression_points(score_model)
regression_points
regression_points %>%
  mutate(squared_residuals = residual^2) %>%
  summarize(sum_of_squared_residuals = sum(squared_residuals))
```
> get_regression_table() function is a wrapper function for some longer code like  

```{r}
library(broom)
library(janitor)
score_model %>%
  tidy(conf.int = TRUE) %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  clean_names() %>%
  rename(lower_ci = conf_low, upper_ci = conf_high)
# more roundabout method of getting the regression table aka get_regression_table
```

> get_regression_points() function is a wrapper function for some longer code like  

```{r}
library(broom)
library(janitor)
score_model %>%
  augment() %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  clean_names() %>%
  select(-c("std_resid", "hat", "sigma", "cooksd", "std_resid"))
```

