---
title: C02_DataIO
author: mia
date: '2022-02-22'
slug: c02-dataio
categories: []
tags: []
---

# import stuff
```{r}
library(tidyverse)
nobel <- read_csv(file = "https://raw.githubusercontent.com/miaamato/tidyverse/main/nobel.csv")
nobel
```
# writing a file
> did not let me write in the file from the github repos, said it was read only  

```{r}
df <- tribble(
  ~x, ~y,
  1, "a", 
  2, "b", 
  3, "c"
)
read.csv(file = "https://raw.githubusercontent.com/miaamato/tidyverse/main/df.csv")
```
# exc1
```{r}
sales <- read.csv(file = "https://raw.githubusercontent.com/miaamato/tidyverse/main/sales.csv")
sales
nobel
```

## stem
```{r}
nobel_stem <- nobel %>%
  filter(category %in% c("Medicine", "Chemistry", "Economics", "Physics"))
nobel_stem
```
## nonstem
```{r}
nobel["category"]
nobel_nonstem <- nobel %>%
  filter(category %in% c("Peace", "Literature"))
nobel_nonstem
```

# badnames Data
```{r}
edibnb_badnames <- read.csv("https://raw.githubusercontent.com/miaamato/tidyverse/main/edibnb-badnames.csv")
names(edibnb_badnames)
```
```{r}
library(ggplot2)
ggplot(edibnb_badnames, aes(Number.of.bathrooms, Price)) +
  geom_point()
# data had periods where the exercise says the names have spaces?
```
## redefine columns
```{r}
edibnb_col_names <- read.csv("https://raw.githubusercontent.com/miaamato/tidyverse/main/edibnb-badnames.csv", 
                             col.names = c("id", "price", "neighborhood", "accomodates", "bathroom", "bedroom", "bed", "review_scores_rating", "n_reviews", "url"))
names(edibnb_col_names)
```
```{r}
edibnb_clean_names <- read.csv('https://raw.githubusercontent.com/miaamato/tidyverse/main/edibnb-badnames.csv') %>%
  janitor::clean_names()
# replaces any spaces with underscores, needs janitor package
names(edibnb_clean_names)
```
## types of columns 
> col character()  
> col_date()  
> col_datetime()  
> col_double()  
> col_factor()  
> col_guess()- default  
> col_integer()  
> col_logical()  
> col_number()- numbers and nonnumbers  
> col_numeric()- double/integer  
> col_skip()- don't read  
> col_time()  


```{r}
read.csv("https://raw.githubusercontent.com/miaamato/tidyverse/main/df-na.csv")

# for some reason does not identify y or z as a variable, tried typeof() and did not work 
# could identify x as character but created error when knitting
```

# Reading from Excel
```{r}
# install package of readxl
library(readxl)
fav_food <- read_excel(file.choose())
fav_food
```
## variable name change
```{r}
library(tidyverse)
fav_food <- read_excel(file.choose()) %>%
  janitor::clean_names()

fav_food
```

## dealing with N/A
```{r}
fav_food <- read_excel(file.choose(),
                       na = c("N/A", "99999")) %>%
  janitor::clean_names()
fav_food
```
## making age numeric

```{r}
av_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
    )
glimpse(fav_food)
```
```{r}
fav_food <- fav_food %>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))
# organizes by the labels

fav_food %>%
  count(ses)
```
## putting all together

```{r}
fav_food <- read_excel(file.choose(), na = c("N/A", "99999")) %>%
  janitor::clean_names() %>%
  mutate(
    age = if_else(age == "five", "5", age), 
    age = as.numeric(age),
    ses = fct_relevel(ses, "Low", "Middle", "High")
  )


fav_food
```
# RDS files
> Like CSVs but not  
> Allows for reading with read_rds() and writing with r write_rds()  

# Sales data exercise
```{r}
sales_ex <- read_excel(file.choose()) 
sales_ex
```

```{r}
colnames(sales_ex) <- c("col1", "col2")
sales_ex <- sales_ex %>%
  mutate(
    brand = case_when(col1 == "Brand 1" ~ "Brand 1",
                      col1 =="Brand 2" ~ "Brand 2",
                      col2 == c("8", "2") ~ "Brand 1",
                      col2 == c("1", "6", "5") ~ "Brand 2") 
    )
sales_ex
```

```{r}
sales_ex[7,3] <- "Brand 1"
sales_ex[10,3] <- "Brand 2"
sales_ex[9,3] <-"Brand 2"
sales_ex

```


```{r}
sales_ex %>%
  filter(col1 != "Brand 1" & col1 != "Brand 2")
```
```{r}
sales_ex %>%
  mutate(
    brand = case_when(col1 == "Brand 1" ~ "Brand 1",
                      col1 =="Brand 2" ~ "Brand 2",
                      col2 == c("8", "2") ~ "Brand 1",
                      col2 == c("1") ~ "Brand 2"),
    id = case_when(col1 != "Brand 1" ~ col1,
                   col1 != "Brand 2" ~ col1)
    )
```

mutate(
    brand = if_else( == "five", "5", age),