---
title: correct A02
author: Mia
date: '2022-04-13'
slug: correct-a02
categories: []
tags: []
---

```{r}
# Opening CSV file reading
library(readxl)
prof_props <- read.csv("https://raw.githubusercontent.com/miaamato/Data/main/profprop.csv")
prof_props
```
## Loading/Opening packages for linear regression
```{r}
library(boot)
# install.packages('ISLR')
library(ggplot2)
library(ISLR)
library(dplyr)
```

```{r}
glimpse(prof_props)

```

### Prep
```{r}
attach(prof_props)
```

## Attempt to transform descriptive data into metric
>> Also removed last row because of the NA value and had to make Price into double  

```{r}
# prof_props
prof_props$Certification <- as.factor(Certification)
prof_props$Clarity <- as.factor(Clarity)
prof_props$Cut <- as.factor(Cut)
prof_props$Symmetry <- as.factor(Symmetry)
prof_props$Wholesaler <- as.factor(Wholesaler)
prof_props$Polish <- as.factor(Polish)
prof_props$Colour <- as.factor(Colour)
prof_props$Price <- as.factor(Price)
prof_props$Price <- as.numeric(gsub('[$,]', '', prof_props$Price))
prof_props <- na.omit(prof_props)
glimpse(prof_props)
```

# Frequency Distribution
### Certification
```{r}
count(prof_props, Certification)
```
```{r}
ggplot(prof_props, aes(x = Certification, fill = Certification)) +
  geom_histogram(binwidth = 20, stat = "count") +
  scale_fill_hue(c=45, l=80)
```
### Clarity  
```{r}
count(prof_props, Clarity)
```
```{r}
ggplot(prof_props, aes(x = Clarity, fill = Clarity)) +
  geom_histogram(binwidth = 20, stat = "count")+
  scale_fill_hue(c=45, l=80)
```

### Cut
```{r}
count(prof_props, Cut)
```
```{r}
ggplot(prof_props, aes(x = Cut, fill = Cut)) +
  geom_histogram(binwidth = 20, stat = "count") +
  scale_fill_hue(c=45, l=80)
```

### Symmetry
```{r}
count(prof_props, Symmetry)
```
```{r}
ggplot(prof_props, aes(x = Symmetry, fill = Symmetry)) +
  geom_histogram(binwidth = 20, stat = "count") +
  scale_fill_hue(c=45, l=80)
```
### Wholesaler  
* Won't have impact on quality of diamond  

```{r}
count(prof_props, Wholesaler)
```

```{r}
ggplot(prof_props, aes(x = Wholesaler, fill = Wholesaler)) +
  geom_histogram(binwidth = 20, stat = "count") +
  scale_fill_hue(c=45, l=80)
```

### Polish
```{r}
count(prof_props, Polish)
```
```{r}
ggplot(prof_props, aes(x = Polish, fill = Polish)) +
  geom_histogram(binwidth = 20, stat = "count") +
  scale_fill_hue(c=45, l=80)
```

### Colour
```{r}
count(prof_props, Colour)
```
```{r}
ggplot(prof_props, aes(x = Colour, fill = Colour)) +
  geom_histogram(binwidth = 20, stat = "count") +
  scale_fill_hue(c=45, l=80)
```
### Carat  
* Already numeric  

```{r}
ggplot(prof_props, aes(x = Carat, fill = Carat)) +
  geom_histogram(binwidth = 20, stat = "count") +
  scale_fill_hue(c=45, l=80)
```
```{r}
count(prof_props, Carat)
```
Analysis: The model produced from the given frequency analysis will allow each category of each variable to be modeled but wholesaler is considered insignificant as price doesn't vary depending on it.

# Linear Model Fitting

```{r}
lm.fit <- lm(Price~Carat + Colour + Cut + Clarity + Certification + Symmetry + Polish , data = prof_props)
summary(lm.fit)
# Price had to be converted to numeric for summary() to function
```
# Using model to predict the professor's diamond
```{r}
perfect <- data.frame(Carat =  0.9,Cut = "V", Colour = "J", Clarity = "SI2", Polish = "G", Symmetry = "V", Certification = "GIA")
perfect
```

```{r}
perfect$Cut <- as.factor(perfect$Cut)
perfect$Colour <- as.factor(perfect$Colour)
perfect$Clarity <- as.factor(perfect$Clarity)
perfect$Polish <- as.factor(perfect$Polish)
perfect$Symmetry <- as.factor(perfect$Symmetry)
perfect$Certification <- as.factor(perfect$Certification)
perfect
```

## Possible predicted value of the ring based on the given criteria
>> The lm.fit model produced this price of the diamond he desired     

```{r}
predict(lm.fit, perfect)
```

# Bootstrap Val 1
```{r}
boot.func <- function(data, index){
return(coef(lm(Price ~ Carat , data = prof_props, subset = index)))
}
set.seed(1)
boot.func(prof_props, 1:440)
boot.func(prof_props, sample(440, 440, replace=T))
boot.out <- boot(prof_props, boot.func, 1000)
```
```{r}
plot(boot.out)
```

# Bootstrap Val 2
```{r}
boot.func <- function(data, index){
return(coef(lm(Price ~ Certification , data = prof_props)))
}
set.seed(1)
boot.func(prof_props, 1:440)
boot.func(prof_props, sample(440, 440, replace=T))
boot.out2 <- boot(prof_props, boot.func, 1000)
```
```{r}
boot.out2
```
# Bootstrap Val 3
```{r}
boot_func <- function(data, index) {
  fit <- coef(lm(Price ~ Colour, data = prof_props, subset = index))
}
int <- boot_func(prof_props, 1:440)
int
set.seed(1)
boot_func(prof_props, sample(440,440, replace = T))
boot.out3 <- boot(prof_props, boot_func, 1001)
```
```{r}
plot(boot.out3)
```
# Bootstrap Val 4
```{r}
boot_func <- function(data, index) {
  fit <- coef(lm(Price ~ Symmetry, data = prof_props,))
}
int <- boot_func(prof_props, 1:440)
int
set.seed(1)
boot_func(prof_props, sample(440,440, replace = T))
boot.out4 <- boot(prof_props, boot_func, 1001)
boot.out4
```

# Bootstrap Val 5
```{r}
boot_func <- function(data, index) {
  fit <- coef(lm(Price ~ Clarity, data = data))
}
set.seed(1)
boot_func(prof_props, sample(440,440, replace = T))
boot.out5 <- boot(prof_props, boot_func, 1001)
boot.out5
```

# Bootstrap Val 6
```{r}
boot_func <- function(data, index) {
  fit <- coef(lm(Price ~ Cut, data = data))
}
int <- boot_func(prof_props, 1:440)
int
set.seed(1)
boot_func(prof_props, sample(440,440, replace = T))
boot.out66 <- boot(prof_props, boot_func, 1001)
boot.out66
```
>>> with subset  

```{r}
boot_func <- function(data, index) {
  fit <- coef(lm(Price ~ Cut, data = data, subset = index))
}
int <- boot_func(prof_props, 1:440)
int
set.seed(1)
boot_func(prof_props, sample(440,440, replace = T))
boot.out6 <- boot(prof_props, boot_func, 1001)
boot.out6
```

```{r}
plot(boot.out6)
```

# Bootstrp 7

```{r}
boot_func <- function(data, index) {
  fit <- coef(lm(Price ~ Wholesaler, data = data))
}
int <- boot_func(prof_props, 1:440)
int
set.seed(1)
boot_func(prof_props, sample(440,440, replace = T))
boot.out88 <- boot(prof_props, boot_func, 1001)
boot.out88
```
>> with subset  

```{r}
boot_func <- function(data, index) {
  fit <- coef(lm(Price ~ Wholesaler, data = data, subset = index))
}
int <- boot_func(prof_props, 1:440)
int
set.seed(1)
boot_func(prof_props, sample(440,440, replace = T))
boot.out8 <- boot(prof_props, boot_func, 1001)
boot.out8
```
```{r}
plot(boot.out8)
```

