---
title: "RMarkdown"
author: "Mia"
date: "2/16/2022"
output:
  html_document:
    theme: yeti
    highlight: zenburn
    df_print: paged
    toc: yes
    toc_float: yes
  theme: default
---

```{r eval= FALSE}
library(datasets)
library(tidyverse)
data(iris)
#load packages
pkgs<- c("rstatix", "emmeans", "psych", "tidyr", "tidyverse", "psych", "dplyr", "ggplot2", "lm.beta", "car", "Hmisc", "skimr", "janitor")
lapply(pkgs, library, character.only = TRUE)
setwd("/Users/amoam/Desktop")
```

# Intro
```{r}
library(datasets)
library(tidyverse)
data(iris)
2+2
mean(iris$Sepal.Length)
```
# Basics
## Inline code
Two plus two `r 2+2`

## Text
two spaces after a line..  
*italics* and _italics_  
**bold** and _bold_  
superscript^2^  
~~strikethrough~~  
[link](github.com)  

## Headers (level2)
## Symbols
inline equation $A = \pi*r^{2}$  

***
> block quote  

* bullet points 
  sub items with tab indentation  
  
## Displaying text
echo = TRUE is default- will show code  
echo = FALSE will not show code, only output  
warning = TRUE will show warnings if any  
warning = FALSE will not  
same with error  
results = TRUE shows output  
results = FALSE does not show output  
eval = TRUE/FALSE whether to evaluate code and include results - aka commenting out  
^^ appears in the ```r part of the chunks  

# Floating TOC
```{r, eval = FALSE}
title: "RMarkdown"
author: "Mia"
date: "2/16/2022"
output: 
  html_document
    theme: yeti
    highlight: zenburn
    df_print: paged
    toc: true
    toc_float: true
    smooth_scroll: true
```

# Advanced Inline Code
```{r}
# run anova
model <- aov(Sepal.Length~Species, data = iris)
summary(model)

# clean tibble from output w broom package
library(broom)
modelmatrix <- broom::tidy(model)

# round to 3 decimals for clean output
modelmatrix$p.value <- sprintf(modelmatrix$p.value, fmt = "%#.3f")
modelmatrix
```

>There is a significant main effect on Species on Sepal Length, *F* `r modelmatrix$df[1]`, `r modelmatrix$df[2]` = `r modelmatrix$statistic[1]`, *p* = `r modelmatrix$p.value[1]`
```{r}

```

