---
title: A04
author: Mia
date: '2022-04-14'
slug: a04
categories: []
tags: []
---
**Appended Graph Analysis**  
The appended visualization shows a bias in the data by having different y-axis ranges for no mask and mask counties. It gives the impression that the cases of COVID-19 are within the same ranges between the mask counties and non mask counties. It's only usefulness could come from being able to demonstrate the rate of cases over time. The graph is overall not effective since the peak of no mask counties is at about 10 units while on the mask county's axis this translates to 21 units.   

## Prep  

```{r}
library(tidyverse)
```

## Data Frame Construction  

```{r}
masked <- tribble(
  ~ date , ~masked,
  "7/12/2020", 25.5,
  "7/13/2020", 19.8,
  "7/14/2020", 19.8,
  "7/15/2020", 20.5,
  "7/16/2020", 19.8,
  "7/17/2020", 19.8,
  "7/18/2020", 20.5,
  "7/19/2020", 19.9,
  "7/20/2020", 20.7,
  "7/21/2020", 21.2,
  "7/22/2020", 19.8,
  "7/23/2020", 19.8,
  "7/24/2020", 20.5,
  "7/25/2020", 19.0,
  "7/26/2020", 19.7,
  "7/27/2020", 17.0,
  "7/28/2020", 16.2,
  "7/29/2020", 16.4,
  "7/30/2020", 16.5,
  "7/31/2020", 16.0,
  "8/1/2020", 16.1,
  "8/2/2020", 15.8,
  "8/3/2020", 15.9
)
```
```{r}
unmasked <- tribble(
  ~ date , ~unmasked,
  "7/12/2020", 9.9,
  "7/13/2020", 9.1,
  "7/14/2020", 9.6,
  "7/15/2020", 9.9,
  "7/16/2020", 9.92,
  "7/17/2020", 9.6,
  "7/18/2020", 9.6,
  "7/19/2020", 9.1,
  "7/20/2020", 8.5,
  "7/21/2020", 8.5,
  "7/22/2020", 8.6,
  "7/23/2020", 8.5,
  "7/24/2020", 9.9,
  "7/25/2020", 9.92,
  "7/26/2020", 10.02,
  "7/27/2020", 9.7,
  "7/28/2020", 9.72,
  "7/29/2020", 9.74,
  "7/30/2020", 10.0,
  "7/31/2020", 8.9,
  "8/1/2020", 9.0,
  "8/2/2020", 8.9,
  "8/3/2020", 9.2
)
```
```{r}
full <- left_join(masked, unmasked)
full
```
## Plotting  

```{r}
ggplot(full, aes(date, group = 1)) + 
  geom_line(aes(y = masked, colour = "masked")) + 
  geom_line(aes(y = unmasked, colour = "unmasked")) +
  labs(
    x = "Date",
    y = "Units of Infected Individuals"
  )
```
**New Graph Analysis**  
The consistent y-axis for both the masked and unmasked COVID-19 infection rates effectively relays, accurately, the population of infected for the given date. There is no misrepresentation of the population size of masked versus unmasked infected populations by a confusing y-axis system

**Impact**  
COVD-19 spread can decrease by the usage of masks while the rate of infection is consistent over time for unmasked counties. However, the overall population of infected individuals has been lower for the unmasked counties versus the masked.

### Video Summary on Cambridge Analytica Interview  

>> This was an interview with one of the employees of Cambridge Analytica, Christopher Wylie. He spoke of his time working under Alexander Nix where he spoke of the set up where he tried to validate his successes to Steve Bannon by faking a Cambridge branch for data analytics. Steve came up with the name of "Cambridge Analytica." This was sort of a con to Steve and then how the world viewed Nix's company. The technique they used to begin electoral influence was through political microtargetting combined with psychological contexts. They received millions of dollars of funding to begin this huge data collection project.  

>> Kogen joined their team which introduced a social networking aspect to this discrete data collection. This was an invasion of privacy to all because nobody knew it was occurring and having knowledge of one individual's profile would automatically allow all of their social media "friends'" profiles to be known. Cambridge Analytica delved into Facebook users and got upwards of 60 million profiles' data. These profiles were the foundation of Cambridge Analytica's algorithms for political microtargetting and building psychological profiles. Cambridge Analytica is connected to other institutions that actually create the targetting content and others that actually published the content. The system takes away from public and social discussions on politics which has led to many niche political rabbit holes creating a severe drift (extremism, partisanship) between the two major parties in the US.


